\documentclass[11pt]{article}

\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsmath,proof,amsthm,amssymb,color}

\newcommand{\nat}{\mathbb{N}}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\boxinate}[1]{\framebox[1.1\width]{#1}}
\newcommand{\blackslash}{\text{\textbackslash}}
\newcommand{\tand}{~\land~}
\newcommand{\tor}{~\lor~}
\newcommand{\diam}{\mathtt{diam}}

\begin{document}

\begin{center}
  {\LARGE 21-355 Lemmas} \\
    \today
\end{center}

\section{Initial Theorems/Definitions}
These are things we should be fairly comfortable with.
\begin{itemize}
\item Defn: $X$ a metric space. If $\forall E \subseteq X, E \neq \emptyset$
  and $E$ bounded from above, then $\sup E \in X$
\item $\forall\;r_1,r_2.\; \exists\;q.\; r_1 < q < r_2$
\item Cauchy Schwartz: $|\langle x, y \rangle| \leq ||x|| ||y||$
\item Union of countable sets is countable. Infinite subset of countable set is
  countable.
\item Limit point: $p$ is a limit point if $\forall\;r > 0.~\exists~q \neq p, q
  \in N_r(p) \land q \in E$
\item Closed: E is closed if $\forall~p$ a limit point of E, $p \in E$
\item Interior Point: $p$ is an interior point in E if $\exists~r > 0.~ N_r(p)
  \subseteq E$
\item Open: $E$ is open if every point is an interior point
\item Sequences must be countable.
\item $S$ has the least upper bound property if $\forall\;E \neq \emptyset, E
  \subseteq S$, E is bound above and $\sup~E \in S$
\item Every neighbourhood is open
\item $\{ G_n \}$ open $\implies \bigcup_n G_n$ open
\item $\{ G_n \}$ closed $\implies \bigcap_n G_n$ closed
\item $\{ G_n \}_{n=1}^{N}$ open $\implies \bigcap_{n = 1}^N G_n$ open
\item $\{ G_n \}_{n=1}^{N}$ closed $\implies \bigcap_{n = 1}^N G_n$ closed
\end{itemize}

\section{Sequences} % Brian

\begin{itemize}
\item $\{p_i\} $ \boxinate{converges} to $p$ $ \iff \exists p \in X . \forall \epsilon
  > 0 . \exists n_0 \in \nat . \forall n \geq n_0 . d(p_n, p) < \epsilon$.

\item $\{p_i\}$ is \boxinate{bounded} $ \iff \exists p \in X . \exists m > 0
  . \forall n \in \nat . d(p_n, p) < m$

\item Some propositions about convergence.
  \begin{itemize}
  \item $p_n \rightarrow p \in X \iff \forall r > 0 . |N_r(p) \blackslash
    \{p_n\}|$ is infinite.


  \item $\{p_i\}$ converges $\implies \{p_i\}$ is bounded.

  \item $E \subset X \tand p$ is a limit point of $E \implies \exists \{p_i\}
    \subset E . p_n \rightarrow p$.

  \end{itemize}

\item If $\{n_i\}$ is a sequence in $\nat$ such that $\forall i \in \nat . n_i
  < n_{i+1}$, then $\{p_{n_i}\}$ is called a \boxinate{subsequence} of
  $\{p_i\}$.

\item If $\{p_{n_i}\}$ converges, its limit is called a
  \boxinate{subsequential limit}.

\item $p_i \rightarrow p \iff \forall \{p_{n_i}\} . p_{n_i} \rightarrow p$.

\item (Bolzano Weirstrauss) $X$ is compact and $\{p_i\} \subseteq X \implies \exists \{p_{n_i}\}
  \subseteq X . \exists p \in X . \{p_{n_i}\} \rightarrow p$.

\item $\{p_i\} \subseteq X$ is a \boxinate{Cauchy sequence} $\iff \forall
  \epsilon > 0 . \exists N_\epsilon . \forall m, n > N_\epsilon . d(p_m, p_n) <
  \epsilon$.

\item $E \subseteq X$, the \boxinate{diameter} of $E$ is
  $$\diam(E) = \sup_{p, q \in E} d(p, q)$$

\item $\diam(\overline{E}) = \diam(E)$
\item $K_n \supseteq K_{n+1} . K_n \neq \emptyset . K_n$ is compact,
  $\lim_{n\rightarrow \infty} \diam(K_n) = 0$, the
  $$\bigcap_{n=1}^\infty K_n$$ contains exactly 1 point.

\item Every convergent sequence is Cauchy.

\item Every Cauchy sequence in a compact metric space $X$ converges to some
  point $p \in X$.

\item Every Cauchy sequence in $\reals^n$ converges.

\item A metric space in which every Cauchy sequence converges is
  \boxinate{complete}.

\item Compact $\implies$ complete.

\item If $\{a_i\}$ is monotonic, it's bounded $\iff$ it's bounded.

\item Let $\{a_i\} \subseteq \reals^n$ Let
  $$E = \{x \in \reals \cup \{+\infty, -\infty\} : \lim_{k\rightarrow \infty}
  a_{n_k} = x\}$$

  Define

  $$\sup E = \overline{\lim_{n\rightarrow\infty}} a_n = \limsup_{n\rightarrow
    \infty} a_n$$

  $$\inf E = \underline{\lim_{n\rightarrow\infty}} a_n = \liminf{n\rightarrow
    \infty} a_n$$

\item $\limsup a_n \in E$.

\item $x > \limsup a_n \implies \exists n \in \nat . \forall i \geq n . a_i <
  x$.

\item $p \in \reals^+ \tand a \in \reals \implies$
  $$\lim_{n \rightarrow \infty} \frac{n^\alpha}{(1+p)^n}$$

\item $\{a_n\} \subseteq [0, \infty)$.
  $$\sum_{n \in \nat} a_n\text{ converges }\iff \{\sum_{i=1}^n a_i\} \text{ is
    bounded}$$

\item $a_1 \geq a_2 \geq a_3 \geq \ldots$ and $0 \leq a_i$.
  $$\sum_{k \in \nat} a_k \text{ converges } \iff \sum_{k \in \nat} 2^k a_{2^k}
  \text{ converges}$$

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%% end of Brian

\section{Compact Metric Spaces} % Rokhini
\begin{itemize}
\item Defn: $\{G_{\alpha}\}$ all open subsets of $X \land E \subseteq \bigcup
  G_{\alpha} \land E \subseteq X \Rightarrow \{G_{\alpha}\}$ is an
  \boxinate{open cover} of $E$

\item Defn: $\forall\;\{G_{\alpha}\}$ such that $E \subseteq \bigcup G_{\alpha}
  ,\;(\exists\;n.\; E \subseteq \bigcup_{\alpha = 1}^n G_{\alpha} \Rightarrow
  E$ is compact)
\item Prop: Closed subsets of compact sets are compact
\item Prop: $E \subseteq X$ where $X$ compact and $|E| = \infty$. Then $E$
  contains a limit point (Heine-Borel)
\item Defn: $A, B \subseteq X$ are separated if $A \cap \overline{B} = B \cap
  \overline{A} = \emptyset$. (Connected = Not separated)
\item $E \subseteq \mathbb{R} \iff ~\forall~x,y \in E$, if $z \in (x, y)$ then
  $z \in E$
\item Prop: $\{I_k\}$ a sequence such that $I_{k+1} \subseteq I_k \forall\;k
  \Rightarrow \bigcap I_k \neq \emptyset$
\item Defn: An $n$ cell is an n-dimensional hypercube defined on $\mathbb{R}^n$
\item Prop: Every ball in $\mathbb{R}^n$ contains an $n$ cell and every $n$
  cell contains a ball
\item Prop: $n$ cells are compact (Proved by contradiction using nested
  quadrants as intervals)
\item Prop: $\{K_{\alpha}\}$ compact and non-empty $\land\; \bigcap_{\alpha =
  1}^n K_{\alpha} \neq \emptyset \Rightarrow \bigcap_{\alpha}^{\infty}
  K_{\alpha} \neq \emptyset$
\item Corollary: $\forall\;j, K_j$ compact and non-empty $\land \;K_{j+1}
  \subseteq K_j \Rightarrow \bigcap_{j=1}^{\infty} K_j \neq
  \emptyset$. Eg. Cantor set
\item Defn: Let $E \subseteq Y \subseteq X$. $E$ is relatively open wrt $Y$ if
  $\forall\;x \in E.\;\exists\;r > 0.\;\{y \in Y: d(x, y) < r\} \subseteq E$
\end{itemize}

\section{Continuity}

\begin{itemize}

\item Let X,Y,Z be metric spaces and $\exists$  X

\item F is said to be $\boxinate{continuous}$ at p $\exists$ if $\forall
  \epsilon >$0, such that if $d_{x}$(x,p) $< \delta$ and x $\in$ X, , then
  $d_y$(F(x),F(p)) $< \epsilon$


\item If F: E $\rightarrow$  Y and G: F(E) $\rightarrow$ Z and h(x) = g(f(x))
  If F,G is continuous at at a point P, then h is cont. at p



\item Prop: F : X $\rightarrow$ Y is cont. $\iff$ $F^{-1}$(V) open for V open


\item Corollary: F is cont. $\iff$ $F^{-1}$(E) is closed if E is closed

\item Let F,G be complex cont. functions in X. Then f+g, fg, $\frac{f}{g}$(g
  $\neq$ 0) are cont. functions.


\item Prop: Let Y be MS, X CMS, if F: X $\rightarrow$ Y is cont., F(X) is
  compact


\item Corollary: X CMS at F: X $\rightarrow \mathbb{R}^k$, then F(x) is closed
  and bounded.

\item Suppose F is a cont. real function on a CMS X and

  $$M = \sup_{p \in X}f(p)$$

  $$m = \inf_{p \in X}f(p)$$

\item Prop: If F: X (CMS) $\rightarrow$ Y (CMS) is a cont. bijection, then
  $F^{-1}$ is cont.

\item Prop: Let F: X (CMS) $\rightarrow$ Y (MS) be a cont. function. Then F is
  uniformly continuous.

\item Prop: Let F: X (CMS) $\rightarrow$ Y be continuous, and E $\subseteq$ X
  be connected. Then F(E) is connected.

\item Corollary: Let F: [a,b) $\rightarrow \mathbb{R}$ be a cont. function. If
  F(a) $<$ F(b) then $\forall$ y s.t. F(a) $<$ y $<$ F(b), $\exists$ c $\in$
  (a,b) such that y = F(c) [IMVT]

\item Prop: Let f be monotonically increasing on (a,b) and x $\in$ (a,b) Then:

  $$ \sup_{a < t < x} f(t) = f(x-) \leq f(x) \leq f(x+) = \inf_{x < t < b}
  f(t) $$

\item Corollary: Monotonic functions have at most a countable set of jump
  discontinuities [Monotonic functions only have jump disconts.?]

\end{itemize}

\end{document}
